### 2021-06-21 src/paper/report.tex
Fix numbers for relative effects (still old seasonality).

% Reports (up to ~2500 words including references, notes and captions–corresponds to ~3
% printed pages in the journal) present important new research results of broad
% significance. Reports should include an abstract, an introductory paragraph, up to
% four figures or tables, and about 30 references. Materials and Methods should be
% included in supplementary materials, which should also include information needed to
% support the paper's conclusions.

% Main Text is not divided into sub-headings for Reports.

% The manuscript should start with a brief introduction describing the paper’s
% significance. The introduction should provide sufficient background information to
% make the article intelligible to readers in other disciplines, and sufficient context
% that the significance of the experimental findings is clear.

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/full_decomposition_channels_area}
        % \includegraphics[width=\textwidth]{figures/results/figures/full_decomposition_channels_bar}
        \caption{Decomposition of the difference between the scenario without any of the
            three factors and the main scenario in
            Figure~\ref{fig:2021_scenarios_newly_infected}.}
        \label{fig:2021_scenarios_decomposition}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/full_decomposition_rapid_tests_area}
        % \includegraphics[width=\textwidth]{figures/results/figures/full_decomposition_rapid_tests_bar}
        \caption{Decomposition of the difference between the scenario without rapid
            tests and the main scenario in
            Figure~\ref{fig:2021_scenarios_newly_infected}.}
        \label{fig:2021_scenarios_decomposition_tests}
    \end{subfigure}

@@

Until mid-March, there is no visible difference between the different scenarios.
Seasonality hardly changes, and only few vaccinations or rapid tests were administered.
Even thereafter, the effect of the vaccination campaign is surprisingly small at first
sight. Whether considering recorded or total infections with only one channel active,
the final level is always the highest in case of the vaccination campaign (orange
lines). The Shapley value decomposition shows that vaccinations contribute about 15\% to
the cumulative difference between scenarios. Reasons for this are the slow start---it
took until March~24th until 10\% of the population had received their first vaccination,
the 20\% mark was reached on April 19th---and the focus on older individuals. These
groups contribute less to the spread of the disease than others due to a lower number of
contacts, see Supplementary Material~\ref{subsec:contacts_by_age}. By the end of our
study period, when first-dose vaccination rates reached around 40\% of the population,
the numbers of new cases would have started to decline. It is important to note that the
initial focus of the campaign was to prevent deaths and severe disease. Indeed, the case
fatality was rate considerably lower during the third wave when compared to the second
(4.4\% between October and February and 1.4\% between March and the end of May).

Seasonality has a large effect in slowing the spread of SARS-CoV-2. By May 31, both
observed and recorded cases would be reduced by a factor of four if only seasonality
mattered. However, in this period, cases would have kept on rising throughout, just at a
much lower pace \citep[this is in line with results in][]{Gavenciak2021}. Nevertheless,
we estimate seasonality to be a quantitatively important factor determining the
evolution of the pandemic, explaining most of the early changes and close to 40\% of the
cumulative difference by the end of May.

The largest effect---almost one half when considering the decompositions---comes from
rapid testing. Here, it is crucial to differentiate between recorded cases and actual
cases. Additional testing means that additional infections will be recorded which would
otherwise remain undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this
effect is large. Until late April, recorded cases are higher in the scenario with rapid
testing alone when compared to the setting where none of the three mechanisms are turned
on. Compared to the scenario with vaccinations only, this point is reached around
mid-May and it would be June for the comparison with the seasonality-only scenario. The
effect on total cases, however, is visible immediately in
Figure~\ref{fig:2021_scenarios_newly_infected}. Despite the fact that only 10\%  of the
population performed weekly rapid tests in March on average, new infections on April 1
would be reduced by 53\% relative to the scenario without vaccinations, rapid tests, or
seasonality.

>>>>

@@

    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/full_decomposition_channels_area}
        \caption{Decomposition of the difference between the scenario without any of the
            three factors and the main scenario in
            Figure~\ref{fig:2021_scenarios_newly_infected}.}
        \label{fig:2021_scenarios_decomposition}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.475\textwidth}
        \centering
        \includegraphics[width=\textwidth]{figures/results/figures/full_decomposition_rapid_tests_area}
        \caption{Decomposition of the difference between the scenario without rapid
            tests and the main scenario in
            Figure~\ref{fig:2021_scenarios_newly_infected}.}
        \label{fig:2021_scenarios_decomposition_tests}
    \end{subfigure}

@@

Until mid-March, there is no visible difference between the different scenarios.
Seasonality hardly changes, and only few vaccinations or rapid tests were administered.
Even thereafter, the effect of the vaccination campaign is surprisingly small at first
sight. Whether considering recorded or total infections with only one channel active,
the final level is always the highest in case of the vaccination campaign (orange
lines). The Shapley value decomposition shows that vaccinations contribute 17\% to the
cumulative difference between scenarios. Reasons for this are the slow start---it took
until March~24th until 10\% of the population had received their first vaccination, the
20\% mark was reached on April 19th---and the focus on older individuals. These groups
contribute less to the spread of the disease than others due to a lower number of
contacts, see Supplementary Material~\ref{subsec:contacts_by_age}. By the end of our
study period, when first-dose vaccination rates reached around 40\% of the population,
the numbers of new cases would have started to decline. It is important to note that the
initial focus of the campaign was to prevent deaths and severe disease. Indeed, the case
fatality was rate considerably lower during the third wave when compared to the second
(4.4\% between October and February and 1.4\% between March and the end of May).

Seasonality has a large effect in slowing the spread of SARS-CoV-2. By May 31, both
observed and recorded cases would be reduced by a factor of four if only seasonality
mattered. However, in this period, cases would have kept on rising throughout, just at a
much lower pace \citep[this is in line with results in][]{Gavenciak2021}. Nevertheless,
we estimate seasonality to be a quantitatively important factor determining the
evolution of the pandemic, explaining most of the early changes and 38\% of the
cumulative difference by the end of May.

The largest effect---45\% in the decompositions---comes from rapid testing. Here, it is
crucial to differentiate between recorded cases and actual cases. Additional testing
means that additional infections will be recorded which would otherwise remain
undetected. Figure~\ref{fig:2021_scenarios_recorded} shows that this effect is large.
Until late April, recorded cases are higher in the scenario with rapid testing alone
when compared to the setting where none of the three mechanisms are turned on. Compared
to the scenario with vaccinations only, this point is reached around mid-May and it
would be June for the comparison with the seasonality-only scenario. The effect on total
cases, however, is visible immediately in
Figure~\ref{fig:2021_scenarios_newly_infected}. Despite the fact that only 10\%  of the
population performed weekly rapid tests in March on average, new infections on April 1
would be reduced by 53\% relative to the scenario without vaccinations, rapid tests, or
seasonality.
